---
title: Webscraping in R using Rvest
author: Loren Collingwood
output: html_document
---
    
To harvest text, the webscraping skillset is a must. This vignette introduces 
webscraping in R using the package Rvest. When I was 
growing up, we used Python to webscrape but now that is less necessary. In my 
experience, you cannot always webscrape everything, and a one-size fits all 

## Step 1

Download the [selector gadget](https://selectorgadget.com) chrome extension.

## Step 2

Install then load the Rvest package.

```{r, include = FALSE}
    knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)

options(scipen = 999, digits = 4)
```

```{r}
    # Install R package if you have not done so #
    #install.packages("rvest")

    # Load package into current R session #
    library("rvest")

```

## Step 3 

Select a website you want to scrape and investigate.

1. Investigate whether the particular information you want from the website can be 
scraped.

2. Is the information presented across a series of pages?

3. Is the information possibly in a table?

4. Are there multiple bits of information you want to scrape? i.e., title, author,
date, main body of text. 

5. Think about how you want the data structure to look like when webscraping is complete.
Do you want the text in single .txt files, a single .csv file with columns for 
metadata?

## Step 4

Open the website (if not already open). Click on the selector gadget and begin 
looking for unique html tags that identify what you want to scrape

## Example

[Core Civic or Corrections Corporation of America (CCA)](https://www.corecivic.com/) 
is a private corrections firm publicly traded on the NYSE. The company produces 
newsletters to shareholders publicly available on its website. Let's scrape these.

## Summary

This vignette has provided a brief overview of the workflow for using webscraping 
in R.

- `resolve_missing_vals()`
